---
title: "ANOVA quiz"
output: learnr::tutorial
runtime: shiny_prerendered
description: "Practice what you've learned (learning goal 3)"
---

```{r setup, include=FALSE}
library(learnr)
data <- load.csv()
knitr::opts_chunk$set(echo = FALSE)

tutorial_options(exercise.checker = gradethis::grade_learnr)
```


## Topic 1
*Goal: Practice running aov(...); interpret summary() output table; identify F-stat and p-value from summary() output and come to basic conclusion*

### Exercise

Write question here
```{r use aov(), exercise=TRUE, exercise.lines = 7}
#empty code chunk for user to enter answer (remove this comment before deploy)

#Start your code below!

#Print your conclusion in quotes. Is there sufficient or insufficient evidence to conclude...
print("")

```

```{r use aov()-hint}
#write hint
```

*Use check chunk to create a function which explains answer; not just provides answer*
*Note must use -solution chunk with grade_code()*
```{r use aov()-solution}
#write model solution code
summary(aov(y ~ x, data = data))
```
```{r use aov()-check}
#what the user receives if the code is correct
grade_code("This code is correct...")

grade_result(
  pass_if(~ identical(.result, print("sufficient")), "Correct, ..."),
  fail_if(~ identical(.result, ...), "Incorrect, ..."),
  fail_if(~ identical(.result, ...), "Incorrect,...")
)

```

## Topic 2

### Quiz

*You can include any number of single or multiple choice questions as a quiz. Use the `question` function to define a question and the `quiz` function for grouping multiple questions together.*

Some questions to verify that you understand the purposes of various base and recommended R packages:

```{r quiz}
quiz(
  question("Which package contains functions for installing other R packages?",
    answer("base"),
    answer("tools"),
    answer("utils", correct = TRUE),
    answer("codetools")
  ),
  question("Which of the R packages listed below are used to create plots?",
    answer("lattice", correct = TRUE),
    answer("tools"),
    answer("stats"),
    answer("grid", correct = TRUE)
  )
)
```

