---
title: "ANOVA quiz"
output: learnr::tutorial
runtime: shiny_prerendered
description: "Practice what you've learned (learning goal 3)"
---

```{r setup, include=FALSE}
library(learnr)
data <- load.csv()
knitr::opts_chunk$set(echo = FALSE)

tutorial_options(exercise.checker = gradethis::grade_learnr)
```


## Topic 1
*Goal: Practice running aov(...); interpret summary() output table; identify F-stat and p-value from summary() output and come to basic conclusion*

### Exercise

Write question here
```{r use aov(), exercise=TRUE, exercise.lines = 7}
#empty code chunk for user to enter answer (remove this comment before deploy)

#Start your code below!

#Print your conclusion in quotes. Is there sufficient or insufficient evidence to conclude...
print("")

```

```{r use aov()-hint}
#write hint
```

*Use check chunk to create a function which explains answer; not just provides answer*
*Note must use -solution chunk with grade_code()*
```{r use aov()-solution}
#write model solution code
summary(aov(y ~ x, data = data))
```
```{r use aov()-check}
#what the user receives if the code is correct
grade_code("This code is correct...")

grade_result(
  pass_if(~ identical(.result, print("sufficient")), "Correct, ..."),
  fail_if(~ identical(.result, ...), "Incorrect, ..."),
  fail_if(~ identical(.result, ...), "Incorrect,...")
)

```

## Topic 2

### Quiz

*Have the user answer a group of questions after exmaining image of boxplots and predicting/comparing F-stats; effectively rank them i.e. F-stat_1 > F-stat_2, True or False*

Some questions to verify that you understand the purposes of various base and recommended R packages:

```{r quiz, echo=FALSE}
quiz(caption = "Question 1",
  question("Write question 1 part a here",
    answer("True", message = "Explain why this is not the correct answer"),
    answer("False", correct = TRUE),
  allow_retry = TRUE,
  random_answer_order = TRUE
    ),
  question("Write question 1 part b here",
    answer("True", correct = TRUE, message = "Explain why this is correct..."),
    answer("False", message = "Explain why this is not the correct answer..."),
  allow_retry = TRUE,
  random_answer_order = TRUE
    )
)
```

