---
title: "quiz-plots"
author: "Samantha Owusu"
date: "7/18/2020"
output: html_document
---

## Plan
```{r dataset}
library(tidyverse)
head(mtcars)
diamonds[1:8,]

str(diamonds)
?diamonds

diamonds.long <- diamonds %>%
  filter(color == "E" | color == "F" | color == "G") %>%
  filter(cut == "Very Good", clarity == "VS1" | clarity == "VVS1" | clarity == "VVS2") %>%
  filter(table == 50:59) %>%
  select(depth, color, clarity)
diamonds.long
```
Is there really a difference in the depth of the top three clear diamond groups (of best 4 colors)?

y-axis : depth
x-axis: IF, VVS1, VVS2
4 plots: color

carat == 0.3, cut == "Very Good"

## Plot
```{r, plot}
#with facet

#library(tidy)
#diamonds.long <- diamonds %>%
  #filter(color == "D" | color == "E" | color == "F" | color == "G") %>%
  #filter(cut == "Very Good", clarity == "IF" | clarity == "VVS1" | clarity == "VVS2") %>%
  #filter(table == 50:59) %>%
  #select(depth, color, clarity)
library(ggplot2)
ggplot(data = diamonds.long, aes(y = depth)) + 
  geom_boxplot(aes(color = clarity)) +
  facet_grid(. ~color) +
  theme(axis.text.x = element_blank())


## w/out facet
diamonds.D <- diamonds.long %>%
  filter(color == "D")
diamonds.E <- diamonds.long %>%
  filter(color == "E")
diamonds.F <- diamonds.long %>%
  filter(color == "F")
diamonds.G <- diamonds.long %>%
  filter(color == "G")
diamonds.G
nrow(diamonds.D)
nrow(diamonds.E)
nrow(diamonds.F)
nrow(diamonds.G)

ggplot(data = diamonds.D[sample(x = nrow(diamonds.D), size = 25),], aes(y = depth)) + 
  geom_boxplot(aes(color = clarity)) +
  theme(axis.text.x=element_blank()) +
  ggtitle("Color D") 

set.seed(1)
diamonds.E <- diamonds.E[sample(x = nrow(diamonds.E), size = 50),]
diamonds.F <- diamonds.F[sample(x = nrow(diamonds.E), size = 50),]
diamonds.G <- diamonds.G[sample(x = nrow(diamonds.E), size = 50),]

ggplot(data = diamonds.E, aes(y = depth)) + 
  geom_boxplot(aes(color = clarity)) +
  theme(axis.text.x=element_blank()) +
  ggtitle("Color E") 
ggplot(data = diamonds.F, aes(y = depth)) + 
  geom_boxplot(aes(color = clarity)) +
  theme(axis.text.x=element_blank()) +
  ggtitle("Color F")
ggplot(data = diamonds.G, aes(y = depth)) + 
  geom_boxplot(aes(color = clarity)) +
  theme(axis.text.x=element_blank()) +
  ggtitle("Color G") 

?diamonds
```

##Make my own rnorm data
Plants grown with two different new fertilizers and 1 (control) with just standard soil. Heights recorded as difference/comparison to standard height of _________. We want to know if difference
Population = 100; sampled 50 plots
```{r, data}
# Location 1
Location.A <- matrix(rep("A", times = 150), ncol = 1)
#head(Location.A)
set.seed(1)
control.A <- matrix(rnorm(n = 50, sd = .8), ncol = 1)
treat1.A <- matrix(rnorm(n = 50, sd = .82), ncol = 1)
treat2.A <- matrix(rnorm(n = 50, sd =.98), ncol = 1)

# Location 2
Location.B <- matrix(rep("B", times = 150), ncol = 1)
set.seed(2)
control.B <- matrix(rnorm(n = 50, sd = .69), ncol = 1)
treat1.B <- matrix(rnorm(n = 50, sd = .76), ncol = 1)
treat2.B <- matrix(rnorm(n = 50, sd =.78), ncol = 1)

# Location 3
Location.C <- matrix(rep("C", times = 150), ncol = 1)
set.seed(3)
control.C <- matrix(rnorm(n = 50, sd = .8), ncol = 1)
treat1.C <- matrix(rnorm(n = 50, sd = .86), ncol = 1)
treat2.C <- matrix(rnorm(n = 50, sd =.83), ncol = 1)


#Make Location Column
Location <- rbind(Location.A, Location.B, Location.C)
Location

#Make Treatment Column
TreatmentA <- matrix(rep(c("Control", "Treatment 1", "Treatment 2"), each = 50), ncol = 1)
TreatmentB <- matrix(rep(c("Control", "Treatment 1", "Treatment 2"), each = 50), ncol = 1)
TreatmentC <- matrix(rep(c("Control", "Treatment 1", "Treatment 2"), each = 50), ncol = 1)
Treatment <- rbind(TreatmentA, TreatmentB, TreatmentC)
Treatment

#Make values column
Value <- rbind(control.A, treat1.A, treat2.A, 
               control.B, treat1.B, treat2.B,
               control.C, treat1.C, treat2.C)
head(Value)


# Make dataframe
PlantHeights <- data.frame(Location, Treatment, Value)
head(PlantHeights)

write.csv(PlantHeights, "PlantHeights.csv")
```


## Is github data accessible?
```{r load-data}
library(downloader) 
url <- "https://raw.githubusercontent.com/sowusu08/ANOVA-PlantHeights-Data/master/Data/PlantHeights.csv"
filename <- "PlantHeights.csv" 
download(url, destfile=filename)

PlantHeights <- read.csv("PlantHeights.csv")
head(PlantHeights)
```

## Making boxplots for plant data
```{r, plants-boxplots}
library(ggplot2)
ggplot(data = PlantHeights, aes(y = Value)) + 
  geom_boxplot(aes(color = Treatment)) +
  facet_grid(. ~Location) +
  theme(axis.text.x = element_blank())

```






